HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence.
Importantly, HUME only requires semantically annotating the source sentence,
thus avoiding the annotation of machine-generated text 
and allowing re-use of the source semantic annotation for measuring the quality
of different translations of the same source sentence.
By basing the measure on a direct comparison
of the source and translation we avoid the difficulties engendered by using
reference translations, albeit at the cost of imposing the additional requirement
that the evaluator be proficient in both the source and target languages.
An elaborate comparision of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

We conduct experiments with four language pairs: English-German, English-Polish,
English-Romanian and English-Czech, and report efficiency (time of annotation) and
inter-annotator agreement scores (\secref{sec:experiments}). Efficiency results that HUME
can be annotated in 2--4 minutes, once the UCCA annotation of the source is given,
which is only about five times slower than MEANT, and hence still practical to
employ on a moderate scale. HUME's agreement results are on par with those
of standard sentence-level ranking measures, but unlike them,
HUME's scores do not decrease with longer sentences.\bh{We may
  have to focus more on qualitative aspects, if we just try to sell
  the measure on IAA, then the figures are not stunning. OA: is that OK?}

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
%\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

HUME operates by aggregating human assessments of the translation quality of individual
semantic units in the source sentence.
Importantly, HUME only requires semantically annotating the source sentence,
thus avoiding the annotation of machine-generated text 
and allowing re-use of the source semantic annotation for measuring the quality
of different translations of the same source sentence.
By basing the measure on a direct comparison
of the source and translation we avoid the difficulties engendered by using
reference translations, albeit at the cost of imposing the additional requirement
that the evaluator be proficient in both the source and target languages.
%An elaborate comparison of HUME and HMEANT is given in \secref{sec:hmeant_comp}.

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}) and highlight its benefits over HMEANT
(\secref{sec:hmeant_comp}).
Our experiments with four language pairs: English-German, English-Polish,
English-Romanian and English-Czech (\secref{sec:experiments}) document the
efficiency (time of annotation) and inter-annotator agreement scores for HUME.

% We conduct experiments with four language pairs: English-German, English-Polish,
% English-Romanian and English-Czech, and report efficiency (time of annotation) and
% inter-annotator agreement scores (\secref{sec:experiments}).
% 
% \XXX{The following should go rather to the conclusion}
% Efficiency results that HUME
% can be annotated in 2--4 minutes, once the UCCA annotation of the source is given,
% which is only about five times slower than MEANT, and hence still practical to
% employ on a moderate scale. HUME's agreement results are on par with those
% of standard sentence-level ranking measures, but unlike them,
% HUME's scores do not decrease with longer sentences.\bh{We may
%   have to focus more on qualitative aspects, if we just try to sell
%   the measure on IAA, then the figures are not stunning. OA: is that OK?}
